\documentclass[]{scrreprt}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={References},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\title{References}
\date{}

\begin{document}
\maketitle

\chapter*{References}\label{references}
\addcontentsline{toc}{chapter}{References}

This list contains all items cited in the text. It also contains some
items not directly mentioned, but which nonetheless guided the
development of the project, or might shape its future.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent
\vspace{-2em} \setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in} \setlength{\parskip}{15pt}

\let\oldhypertarget\hypertarget

\renewcommand{\hypertarget}[2]{%
    \penalty 0%
    \oldhypertarget{#1}{#2}%
}

\hypertarget{refs}{}
\hypertarget{ref-allardux5fnewux5f1992}{}
{[}1{]} J.-F. Allard and Y. Champoux, ``New empirical equations for
sound propagation in rigid frame fibrous materials,'' \emph{The Journal
of the Acoustical Society of America}, vol. 91, no. 6, pp. 3346--3353,
1992.

\hypertarget{ref-allenux5fimageux5f1979}{}
{[}2{]} J. B. Allen and D. A. Berkley, ``Image method for efficiently
simulating small-room acoustics,'' \emph{The Journal of the Acoustical
Society of America}, vol. 65, no. 4, pp. 943--950, 1979.

\hypertarget{ref-alpkocakux5fcomputingux5f2010}{}
{[}3{]} A. Alpkocak and M. Sis, ``Computing impulse response of room
acoustics using the ray-tracing method in time domain,'' \emph{Archives
of Acoustics}, vol. 35, no. 4, pp. 505--519, 2010.

\hypertarget{ref-amanatidesux5ffastux5f1987}{}
{[}4{]} J. Amanatides, A. Woo, and others, ``A fast voxel traversal
algorithm for ray tracing,'' in \emph{Eurographics}, 1987, vol. 87, pp.
3--10.

\hypertarget{ref-antoniux5forthogonal-likeux5f2010}{}
{[}5{]} J. Antoni, ``Orthogonal-like fractional-octave-band filters,''
\emph{The Journal of the Acoustical Society of America}, vol. 127, no.
2, pp. 884--895, 2010.

\hypertarget{ref-aretzux5fcombinedux5f2009}{}
{[}6{]} M. Aretz, R. Nöthen, M. Vorländer, and D. Schröder, ``Combined
broadband impulse responses using FEM and hybrid ray-based methods,'' in
\emph{EAA Symposium on Auralization}, 2009.

\hypertarget{ref-bassux5fatmosphericux5f1972}{}
{[}7{]} H. E. Bass, H.-J. Bauer, and L. B. Evans, ``Atmospheric
absorption of sound: Analytical expressions,'' \emph{The Journal of the
Acoustical Society of America}, vol. 52, no. 3B, pp. 821--825, 1972.

\hypertarget{ref-beesonux5froomweaver:ux5f2004}{}
{[}8{]} M. J. Beeson and D. T. Murphy, ``RoomWeaver: A digital waveguide
mesh based room acoustics research tool,'' in \emph{Proc. COST G6 Conf.
Digital Audio Effects (Naples, Italy, October 2004)}, 2004, pp. 268--73.

\hypertarget{ref-murphyux5fkw-boundaryux5f2007}{}
{[}9{]} D. T. Murphy and M. Beeson, ``The KW-boundary hybrid digital
waveguide mesh for room acoustics applications,'' \emph{IEEE
Transactions on Audio, Speech, and Language Processing}, vol. 15, no. 2,
pp. 552--564, 2007.

\hypertarget{ref-bertramux5fphononux5f2005}{}
{[}10{]} M. Bertram, E. Deines, J. Mohring, J. Jegorovs, and H. Hagen,
``Phonon tracing for auralization and visualization of sound,'' in
\emph{VIS 05. IEEE Visualization, 2005.}, 2005, pp. 151--158.

\hypertarget{ref-bilbaoux5fmodelingux5f2013}{}
{[}11{]} S. Bilbao, ``Modeling of complex geometries and boundary
conditions in finite difference/finite volume time domain room acoustics
simulation,'' \emph{IEEE Transactions on Audio, Speech, and Language
Processing}, vol. 21, no. 7, pp. 1524--1533, 2013.

\hypertarget{ref-borishux5fextensionux5f1984}{}
{[}12{]} J. Borish, ``Extension of the image model to arbitrary
polyhedra,'' \emph{The Journal of the Acoustical Society of America},
vol. 75, no. 6, pp. 1827--1836, 1984.

\hypertarget{ref-camposux5fparallelux5f2000}{}
{[}13{]} G. Campos and D. Howard, ``A parallel 3D digital waveguide mesh
model with tetrahedral topology for room acoustic simulation,'' in
\emph{Proceedings of the COST G-6 Conference on Digital Audio Effects
(DAFx),(Verona, Italy)}, 2000, pp. 73--78.

\hypertarget{ref-camposux5fcomputationalux5f2005}{}
{[}14{]} G. R. Campos and D. M. Howard, ``On the computational
efficiency of different waveguide mesh topologies for room acoustic
simulation,'' \emph{IEEE Transactions on Speech and Audio Processing},
vol. 13, no. 5, pp. 1063--1072, 2005.

\hypertarget{ref-christensenux5fnewux5f2005}{}
{[}15{]} C. L. Christensen and J. H. Rindel, ``A new scattering method
that combines roughness and diffraction effects,'' in \emph{Forum
Acousticum, Budapest, Hungary}, 2005.

\hypertarget{ref-deinesux5fcomparativeux5f2006}{}
{[}16{]} E. Deines, M. Bertram, J. Mohring, J. Jegorovs, F. Michel, H.
Hagen, and G. M. Nielson, ``Comparative visualization for wave-based and
geometric acoustics,'' \emph{IEEE Transactions on Visualization and
Computer Graphics}, vol. 12, no. 5, pp. 1173--1180, 2006.

\hypertarget{ref-delanyux5facousticalux5f1970}{}
{[}17{]} M. E. Delany and E. N. Bazley, ``Acoustical properties of
fibrous absorbent materials,'' \emph{Applied acoustics}, vol. 3, no. 2,
pp. 105--116, 1970.

\hypertarget{ref-dimitrijevicux5foptimizationux5f2015}{}
{[}18{]} B. Dimitrijevic, B. Nikolic, S. Aleksic, and N. Raicevic,
``Optimization of Excitation in FDTD Method and Corresponding Source
Modeling,'' \emph{RADIOENGINEERING}, vol. 24, no. 1, p. 11, 2015.

\hypertarget{ref-duranyux5fanalyticalux5f2015}{}
{[}19{]} J. Durany, T. Mateos, and A. Garriga, ``Analytical Computation
of Acoustic Bidirectional Reflectance Distribution Functions,''
\emph{Open Journal of Acoustics}, vol. 5, no. 04, p. 207, 2015.

\hypertarget{ref-vanux5fduyneux5f3dux5f1996}{}
{[}20{]} S. A. Van Duyne and J. O. Smith III, ``The 3D tetrahedral
digital waveguide mesh with musical applications,'' in \emph{Proceedings
of the 1996 International Computer Music Conference}, 1996, pp. 9--16.

\hypertarget{ref-vanux5fduyneux5ftetrahedralux5f1995}{}
{[}21{]} S. A. Van Duyne and J. O. Smith, ``The tetrahedral digital
waveguide mesh,'' in \emph{Applications of Signal Processing to Audio
and Acoustics, 1995., IEEE ASSP Workshop on}, 1995, pp. 234--237.

\hypertarget{ref-fontanaux5fsignal-theoreticux5f2001}{}
{[}22{]} F. Fontana and D. Rocchesso, ``Signal-theoretic
characterization of waveguide mesh geometries for models of
two-dimensional wave propagation in elastic media,'' \emph{IEEE
Transactions on Speech and Audio Processing}, vol. 9, no. 2, pp.
152--161, 2001.

\hypertarget{ref-escolano-carrascoux5fphysicalux5f2006}{}
{[}23{]} J. Escolano-Carrasco and F. Jacobsen, ``A physical
interpretation of frequency dependent boundary conditions in a digital
waveguide mesh,'' in \emph{Proceedings of Thirteenth International
Congress on Sound and Vibration}, 2006.

\hypertarget{ref-fuux5fgpu-basedux5f2016}{}
{[}24{]} Z.-h. Fu and J.-w. Li, ``GPU-based image method for room
impulse response calculation,'' \emph{Multimedia Tools and
Applications}, pp. 1--17, 2016.

\hypertarget{ref-furseux5fproblemux5f2000}{}
{[}25{]} C. M. Furse, D. H. Roper, D. N. Buechler, D. A. Christensen,
and C. H. Durney, ``The problem and treatment of DC offsets in FDTD
simulations,'' \emph{IEEE Transactions on Antennas and Propagation},
vol. 48, no. 8, pp. 1198--1201, 2000.

\hypertarget{ref-gedneyux5fintroductionux5f2011}{}
{[}26{]} S. D. Gedney, ``Introduction to the finite-difference
time-domain (FDTD) method for electromagnetics,'' \emph{Synthesis
Lectures on Computational Electromagnetics}, vol. 6, no. 1, pp. 1--250,
2011.

\hypertarget{ref-gorzelux5fvirtualux5f2010}{}
{[}27{]} M. Gorzel, G. Kearney, F. Boland, and H. Rice, ``Virtual
acoustic recording: An interactive approach,'' in \emph{Proc. of the
13th internation conference on Digital Audio Effects (DAFX). Graz,
Austria}, 2010.

\hypertarget{ref-hacihabibogluux5ftime-domainux5f2008}{}
{[}28{]} H. Hacihabiboglu, B. Gunel, and A. M. Kondoz, ``Time-domain
simulation of directive sources in 3-D digital waveguide mesh-based
acoustical models,'' \emph{IEEE transactions on audio, speech, and
language processing}, vol. 16, no. 5, pp. 934--946, 2008.

\hypertarget{ref-hacihabibogluux5faccuracyux5f2008}{}
{[}29{]} H. Hacihabiboglu, B. Gunel, and A. M. Kondoz, ``On the accuracy
of first-order numerical derivatives in multidimensional digital
waveguide mesh topologies,'' \emph{IEEE Signal Processing Letters}, vol.
15, pp. 9--12, 2008.

\hypertarget{ref-hacihabibogluux5fsimulationux5f2010}{}
{[}30{]} H. Hacıhabiboglu, B. Günel, and Z. Cvetkovic, ``Simulation of
directional microphones in digital waveguide mesh-based models of room
acoustics,'' \emph{IEEE Trans. on Audio, Speech and Language Process},
vol. 18, no. 2, pp. 213--223, 2010.

\hypertarget{ref-hadiux5fdiscreteux5f2010}{}
{[}31{]} M. F. Hadi and N. B. Almutairi, ``Discrete finite-difference
time domain impulse response filters for transparent field source
implementations,'' \emph{IET microwaves, antennas \& propagation}, vol.
4, no. 3, pp. 381--389, 2010.

\hypertarget{ref-hamiltonux5fsamplingux5f2013}{}
{[}32{]} B. Hamilton, ``Sampling and Reconstruction on a Diamond Grid
and the Tetrahedral Digital Waveguide Mesh,'' \emph{IEEE Signal
Processing Letters}, vol. 10, no. 20, pp. 925--928, 2013.

\hypertarget{ref-heinzux5fbinauralux5f1993}{}
{[}33{]} R. Heinz, ``Binaural room simulation based on an image source
model with addition of statistical methods to include the diffuse sound
scattering of walls and to predict the reverberant tail,'' \emph{Applied
Acoustics}, vol. 38, no. 2, pp. 145--159, 1993.

\hypertarget{ref-huopaniemiux5fmodelingux5f1997}{}
{[}34{]} J. Huopaniemi, L. Savioja, and M. Karjalainen, ``Modeling of
reflections and air absorption in acoustical spaces: A digital filter
design approach,'' in \emph{IEEE Workshop on Applications of Signal
Processing to Audio and Acoustics}, 1997, pp. 19--22.

\hypertarget{ref-jeongux5fsourceux5f2012}{}
{[}35{]} H. Jeong and Y. W. Lam, ``Source implementation to eliminate
low-frequency artifacts in finite difference time domain room acoustic
simulation,'' \emph{The Journal of the Acoustical Society of America},
vol. 131, no. 1, pp. 258--268, 2012.

\hypertarget{ref-karjalainenux5fdigitalux5f2004}{}
{[}36{]} M. Karjalainen and C. Erkut, ``Digital waveguides versus finite
difference structures: Equivalence and mixed modeling,'' \emph{EURASIP
Journal on Applied Signal Processing}, vol. 2004, pp. 978--989, 2004.

\hypertarget{ref-kelloniemiux5ffrequency-dependentux5f2006}{}
{[}37{]} A. Kelloniemi, ``Frequency-dependent boundary condition for the
3-D digital waveguide mesh,'' in \emph{Proc. Int. Conf. Digital Audio
Effects (DAFx'06)}, 2006, pp. 161--164.

\hypertarget{ref-kimux5fdomainux5f2009}{}
{[}38{]} M. Kim and G. P. Scavone, ``Domain decomposition method for the
digital waveguide mesh,'' in \emph{2009 IEEE Workshop on Applications of
Signal Processing to Audio and Acoustics}, 2009, pp. 21--24.

\hypertarget{ref-koutsourisux5fcombinationux5f2013}{}
{[}39{]} G. I. Koutsouris, J. Brunskog, C.-H. Jeong, and F. Jacobsen,
``Combination of acoustical radiosity and the image source method,''
\emph{The Journal of the Acoustical Society of America}, vol. 133, no.
6, pp. 3963--3974, 2013.

\hypertarget{ref-kowalczykux5fmodelingux5f2008}{}
{[}40{]} K. Kowalczyk and M. van Walstijn, ``Modeling
frequency-dependent boundaries as digital impedance filters in FDTD and
K-DWM room acoustics simulations,'' \emph{Journal of the Audio
Engineering Society}, vol. 56, no. 7/8, pp. 569--583, 2008.

\hypertarget{ref-kowalczykux5fmodellingux5f2008}{}
{[}41{]} K. Kowalczyk and M. van Walstijn, ``Modelling
Frequency-Dependent Boundaries as Digital Impedance Filters in FDTD Room
Acoustic Simulations,'' in \emph{Audio Engineering Society Convention
124}, 2008.

\hypertarget{ref-kowalczykux5froomux5f2011}{}
{[}42{]} K. Kowalczyk and M. van Walstijn, ``Room acoustics simulation
using 3-D compact explicit FDTD schemes,'' \emph{IEEE Transactions on
Audio, Speech, and Language Processing}, vol. 19, no. 1, pp. 34--46,
2011.

\hypertarget{ref-kuttruffux5froomux5f2009}{}
{[}43{]} H. Kuttruff, \emph{Room Acoustics, Fifth Edition}. CRC Press,
2009.

\hypertarget{ref-lafortuneux5fnon-linearux5f1997}{}
{[}44{]} E. P. Lafortune, S.-C. Foo, K. E. Torrance, and D. P.
Greenberg, ``Non-linear approximation of reflectance functions,'' in
\emph{Proceedings of the 24th annual conference on Computer graphics and
interactive techniques}, 1997, pp. 117--126.

\hypertarget{ref-lehmannux5fpredictionux5f2008}{}
{[}45{]} E. A. Lehmann and A. M. Johansson, ``Prediction of energy decay
in room impulse responses simulated with an image-source model,''
\emph{The Journal of the Acoustical Society of America}, vol. 124, no.
1, pp. 269--277, 2008.

\hypertarget{ref-levyux5fcomplex-curveux5f1959}{}
{[}46{]} E. C. Levy, ``Complex-curve fitting,'' \emph{IRE transactions
on automatic control}, no. 1, pp. 37--43, 1959.

\hypertarget{ref-marbjergux5fdevelopmentux5f2015}{}
{[}47{]} G. Marbjerg, J. Brunskog, C.-H. Jeong, and E. Nilsson,
``Development and validation of a combined phased acoustical radiosity
and image source model for predicting sound fields in roomsa),''
\emph{The Journal of the Acoustical Society of America}, vol. 138, no.
3, pp. 1457--1468, 2015.

\hypertarget{ref-mcgovernux5fimage-sourceux5f2011}{}
{[}48{]} S. McGovern, ``The image-source reverberation model in an
N-dimensional space,'' in \emph{Proc. 14th Int. Conf. Digital Audio
Effects, Paris, France}, 2011, pp. 11--18.

\hypertarget{ref-miklavcicux5fpracticalux5f2004}{}
{[}49{]} S. J. Miklavcic and J. Ericsson, \emph{Practical implementation
of the 3D tetrahedral TLM method and visualization of room acoustics}.
Department of Science; Technology (ITN), Campus Norrköping, Linköping
University {[}Institutionen för teknik och naturvetenskap (ITN), Campus
Norrköping, Linköpings universitet{]}, 2004.

\hypertarget{ref-mouchtarisux5feffcientux5f2002}{}
{[}50{]} A. Mouchtaris, S. S. Narayanan, and C. Kyriakakis, ``Effcient
multichannel audio resynthesis by subband-based spectral conversion,''
in \emph{Signal Processing Conference, 2002 11th European}, 2002, pp.
1--4.

\hypertarget{ref-murphyux5fdigitalux5f2000}{}
{[}51{]} D. T. Murphy and D. M. Howard, ``Digital waveguide mesh
topologies in room acoustics modelling,'' PhD thesis, Citeseer, 2000.

\hypertarget{ref-murphyux5fdigitalux5f2002}{}
{[}52{]} D. T. Murphy and J. Mullen, ``Digital waveguide mesh modelling
of room acoustics: Improved anechoic boundaries,'' in \emph{Proc. DAFX},
2002, vol. 2, pp. 163--168.

\hypertarget{ref-murphyux5fhybridux5f2008}{}
{[}53{]} D. Murphy, M. Beeson, S. Shelley, A. Moore, and A. Southern,
``Hybrid room impulse response synthesis in digital waveguide mesh based
room acoustics simulation,'' in \emph{Proceedings of the 11th
International Conference on Digital Audio Effects (DAFx-08)}, 2008, pp.
129--136.

\hypertarget{ref-murphyux5fsourceux5f2014}{}
{[}54{]} D. T. Murphy, A. Southern, and L. Savioja, ``Source excitation
strategies for obtaining impulse responses in finite difference time
domain room acoustics simulation,'' \emph{Applied Acoustics}, vol. 82,
pp. 6--14, 2014.

\hypertarget{ref-nelsonux5fhigh-speedux5f1972}{}
{[}55{]} G. Nelson, L. Pfeifer, and R. Wood, ``High-speed octave band
digital filtering,'' \emph{IEEE Transactions on audio and
electroacoustics}, vol. 20, no. 1, pp. 58--65, 1972.

\hypertarget{ref-howarthux5fapplicationux5f1998}{}
{[}56{]} M. J. Howarth, ``The application of advanced computer models to
the prediction of sound in enclosed spaces,'' PhD thesis, University of
Salford, 1998.

\hypertarget{ref-orourkeux5ffindingux5f1985}{}
{[}57{]} J. O'Rourke, ``Finding minimal enclosing boxes,''
\emph{International journal of computer \& information sciences}, vol.
14, no. 3, pp. 183--199, 1985.

\hypertarget{ref-oxnardux5ffrequency-dependentux5f2015}{}
{[}58{]} S. Oxnard, D. O'Brien, J. van Mourik, and D. Murphy,
``Frequency-Dependent Absorbing Boundary Implementations in 3D Finite
Difference Time Domain Room Acoustics Simulations,'' 2015.

\hypertarget{ref-revellesux5fefficientux5f2000}{}
{[}59{]} J. Revelles, C. Urena, and M. Lastra, ``An efficient parametric
algorithm for octree traversal,'' 2000.

\hypertarget{ref-rindelux5fmodellingux5f1993}{}
{[}60{]} J. H. Rindel, ``Modelling the angle-dependent pressure
reflection factor,'' \emph{Applied Acoustics}, vol. 38, no. 2, pp.
223--234, 1993.

\hypertarget{ref-rindelux5fuseux5f2000}{}
{[}61{]} J. H. Rindel, ``The use of computer modeling in room
acoustics,'' \emph{Journal of vibroengineering}, vol. 3, no. 4, pp.
41--72, 2000.

\hypertarget{ref-saviojaux5finterpolatedux5f2001}{}
{[}62{]} L. Savioja and V. Valimaki, ``Interpolated 3-D digital
waveguide mesh with frequency warping,'' in \emph{Acoustics, Speech, and
Signal Processing, 2001. Proceedings.(ICASSP'01). 2001 IEEE
International Conference on}, 2001, vol. 5, pp. 3345--3348.

\hypertarget{ref-saviojaux5fdspux5f1996}{}
{[}63{]} L. Savioja, M. Karjalainen, and T. Takala, ``DSP formulation of
a finite difference method for room acoustics simulation,'' in
\emph{Proceedings of NORSIG'96 IEEE Nordic Signal Processing Symposium},
1996, pp. 455--458.

\hypertarget{ref-saviojaux5freductionux5f1999}{}
{[}64{]} L. Savioja and V. Valimaki, ``Reduction of the dispersion error
in the interpolated digital waveguide mesh using frequency warping,'' in
\emph{Acoustics, Speech, and Signal Processing, 1999. Proceedings., 1999
IEEE International Conference on}, 1999, vol. 2, pp. 973--976.

\hypertarget{ref-saviojaux5foverviewux5f2015}{}
{[}65{]} L. Savioja and U. P. Svensson, ``Overview of geometrical room
acoustic modeling techniques,'' \emph{The Journal of the Acoustical
Society of America}, vol. 138, no. 2, pp. 708--730, 2015.

\hypertarget{ref-saviojaux5finterpolatedux5f2014}{}
{[}66{]} L. Savioja, T. Lokki, and V. Välimäki, ``The interpolated 3-D
digital waveguide mesh method for room acoustic simulation and
auralization,'' \emph{Ultragarsas`` Ultrasound''}, vol. 48, no. 3, pp.
48--52, 2014.

\hypertarget{ref-saviojaux5fdigitalux5f2001}{}
{[}67{]} L. Savioja and T. Lokki, ``Digital waveguide mesh for room
acoustic modeling,'' \emph{CAMPFIRE}, vol. 6, no. 3, p. 13, 2001.

\hypertarget{ref-schneiderux5fimplementationux5f1998}{}
{[}68{]} J. B. Schneider, C. L. Wagner, and S. L. Broschat,
``Implementation of transparent sources embedded in acoustic
finite-difference time-domain grids,'' \emph{The Journal of the
Acoustical Society of America}, vol. 103, no. 1, pp. 136--142, 1998.

\hypertarget{ref-schroderux5fphysicallyux5f2011}{}
{[}69{]} D. Schröder, \emph{Physically based real-time auralization of
interactive virtual environments}, vol. 11. Logos Verlag Berlin GmbH,
2011.

\hypertarget{ref-schroederux5fnewux5f1965}{}
{[}70{]} M. R. Schroeder, ``New Method of Measuring Reverberation
Time,'' \emph{The Journal of the Acoustical Society of America}, vol.
37, no. 3, pp. 409--412, Mar. 1965.

\hypertarget{ref-sheafferux5ffdtdux2fk-dwmux5f2010}{}
{[}71{]} J. Sheaffer and B. M. Fazenda, ``FDTD/K-DWM simulation of 3D
room acoustics on general purpose graphics hardware using compute
unified device architecture (CUDA),'' \emph{Proc. Institute of
Acoustics}, vol. 32, no. 5, 2010.

\hypertarget{ref-sheafferux5fmodellingux5f2013}{}
{[}72{]} J. Sheaffer, C. Webb, and B. M. Fazenda, ``Modelling binaural
receivers in finite difference simulation of room acoustics,'' in
\emph{Proceedings of Meetings on Acoustics}, 2013, vol. 19, p. 015098.

\hypertarget{ref-sheafferux5fphysicalux5f2014}{}
{[}73{]} J. Sheaffer, M. van Walstijn, and B. Fazenda, ``Physical and
numerical constraints in source modeling for finite difference
simulation of room acousticsa),'' \emph{The Journal of the Acoustical
Society of America}, vol. 135, no. 1, pp. 251--261, 2014.

\hypertarget{ref-sheafferux5fbinauralux5f2015}{}
{[}74{]} J. Sheaffer, M. Van Walstijn, B. Rafaely, and K. Kowalczyk,
``Binaural reproduction of finite difference simulations using spherical
array processing,'' \emph{IEEE/ACM Transactions on Audio, Speech, and
Language Processing}, vol. 23, no. 12, pp. 2125--2135, 2015.

\hypertarget{ref-sheafferux5fsourceux5f2013}{}
{[}75{]} J. Sheaffer, ``From source to brain: Modelling sound
propagation and localisation in rooms,'' PhD thesis, Citeseer, 2013.

\hypertarget{ref-shelleyux5fdiffuseux5f2007}{}
{[}76{]} S. B. Shelley, \emph{Diffuse boundary modelling in the digital
waveguide mesh}. University of York, 2007.

\hypertarget{ref-shelleyux5fdiffusionux5f2005}{}
{[}77{]} S. Shelley and D. T. Murphy, ``Diffusion modelling at the
boundary of a digital waveguide mesh,'' in \emph{Signal Processing
Conference, 2005 13th European}, 2005, pp. 1--4.

\hypertarget{ref-funkhouserux5fbeamux5f1998}{}
{[}78{]} T. Funkhouser, I. Carlbom, G. Elko, G. Pingali, M. Sondhi, and
J. West, ``A beam tracing approach to acoustic modeling for interactive
virtual environments,'' in \emph{Proceedings of the 25th annual
conference on Computer graphics and interactive techniques}, 1998, pp.
21--32.

\hypertarget{ref-siltanenux5froomux5f2007}{}
{[}79{]} S. Siltanen, T. Lokki, S. Kiminki, and L. Savioja, ``The room
acoustic rendering equation,'' \emph{The Journal of the Acoustical
Society of America}, vol. 122, no. 3, pp. 1624--1635, 2007.

\hypertarget{ref-siltanenux5fmodelingux5f2012}{}
{[}80{]} S. Siltanen, T. Lokki, S. Tervo, and L. Savioja, ``Modeling
incoherent reflections from rough room surfaces with image sources,''
\emph{The Journal of the Acoustical Society of America}, vol. 131, no.
6, pp. 4606--4614, 2012.

\hypertarget{ref-siltanenux5ffinite-differenceux5f2013}{}
{[}81{]} S. Siltanen, A. Southern, and L. Savioja, ``Finite-difference
time domain method source calibration for hybrid acoustics modeling,''
in \emph{2013 IEEE International Conference on Acoustics, Speech and
Signal Processing}, 2013, pp. 166--170.

\hypertarget{ref-smithux5fphysicalux5f1992}{}
{[}82{]} J. O. Smith, ``Physical modeling using digital waveguides,''
\emph{Computer music journal}, vol. 16, no. 4, pp. 74--91, 1992.

\hypertarget{ref-southernux5f2ndux5f2007}{}
{[}83{]} A. Southern and D. T. Murphy, ``2nd order spherical harmonic
spatial encoding of digital waveguide mesh room acoustic models,'' in
\emph{Proceedings of the 10th International Conference on Digital Audio
Effects (DAFx07), Bordeaux, France}, 2007, pp. 101--108.

\hypertarget{ref-southernux5fmethodsux5f2007}{}
{[}84{]} A. Southern and D. Murphy, ``Methods for 2 nd Order Spherical
Harmonic Spatial Encoding in Digital Waveguide Mesh Virtual Acoustic
Simulations,'' in \emph{2007 IEEE Workshop on Applications of Signal
Processing to Audio and Acoustics}, 2007, pp. 203--206.

\hypertarget{ref-southernux5fspatialux5f2011}{}
{[}85{]} A. Southern, S. Siltanen, and L. Savioja, ``Spatial room
impulse responses with a hybrid modeling method,'' in \emph{Audio
Engineering Society Convention 130}, 2011.

\hypertarget{ref-southernux5froomux5f2013}{}
{[}86{]} A. Southern, S. Siltanen, D. T. Murphy, and L. Savioja, ``Room
impulse response synthesis and validation using a hybrid acoustic
model,'' \emph{IEEE Transactions on Audio, Speech, and Language
Processing}, vol. 21, no. 9, pp. 1940--1952, 2013.

\hypertarget{ref-southernux5fhybridux5f2013}{}
{[}87{]} A. Southern and S. Siltanen, ``A hybrid acoustic model for room
impulse response synthesis,'' in \emph{Proceedings of Meetings on
Acoustics}, 2013, vol. 19, p. 015113.

\hypertarget{ref-summersux5fassessingux5f2004}{}
{[}88{]} J. E. Summers, K. Takahashi, Y. Shimizu, and T. Yamakawa,
``Assessing the accuracy of auralizations computed using a hybrid
geometrical-acoustics and wave-acoustics method,'' \emph{The Journal of
the Acoustical Society of America}, vol. 115, no. 5, pp. 2514--2515,
2004.

\hypertarget{ref-bilbaoux5fgridux5f2009}{}
{[}89{]} S. Bilbao, ``Grid Functions and Finite Difference Operators in
2D,'' in \emph{Numerical Sound Synthesis}, John Wiley \& Sons, Ltd,
2009, pp. 287--304.

\hypertarget{ref-foteinouux5fhybridux5f2014}{}
{[}90{]} A. Foteinou, J. Van Mourik, S. Oxnard, and D. Murphy, ``Hybrid
Acoustic Modelling of Historic Spaces Using Blender,'' 2014.

\hypertarget{ref-vorlanderux5fauralization:ux5f2007}{}
{[}91{]} M. Vorländer, \emph{Auralization: Fundamentals of acoustics,
modelling, simulation, algorithms and acoustic virtual reality}.
Springer Science \& Business Media, 2007.

\hypertarget{ref-vorlanderux5fsimulationux5f2009}{}
{[}92{]} M. Vorlander, ``Simulation and auralization of broadband room
impulse responses,'' in \emph{Tecniacústica 2009}, 2009.

\hypertarget{ref-warrenux5fnumericalux5f1998}{}
{[}93{]} G. S. Warren and W. R. Scott, ``Numerical dispersion in the
finite-element method using three-dimensional edge elements,''
\emph{Microwave and Optical Technology Letters}, vol. 18, no. 6, pp.
423--429, 1998.

\hypertarget{ref-zhangux5fefficientux5f2001}{}
{[}94{]} C. Zhang and T. Chen, ``Efficient feature extraction for 2D/3D
objects in mesh representation,'' in \emph{Image Processing, 2001.
Proceedings. 2001 International Conference on}, 2001, vol. 3, pp.
935--938.

\hypertarget{ref-ux5feaseux5f2016}{}
{[}95{]} ``EASE.'' 2016 {[}Online{]}. Available:
\url{http://ease.afmg.eu/index.php/features.html}. {[}Accessed:
05-Dec-2016{]}

\hypertarget{ref-ux5faudiobornux5f2016}{}
{[}96{]} ``Audioborn.'' 2016 {[}Online{]}. Available:
\url{http://www.audioborn.com}. {[}Accessed: 05-Dec-2016{]}

\hypertarget{ref-ux5fotlux5f2016}{}
{[}97{]} ``OTL.'' 2016 {[}Online{]}. Available:
\url{http://www.olivetreelab.com/Room}. {[}Accessed: 05-Dec-2016{]}

\hypertarget{ref-ux5fi-simpaux5f2016}{}
{[}98{]} ``I-Simpa,'' \emph{I-Simpa}. 2016 {[}Online{]}. Available:
\url{http://i-simpa.ifsttar.fr/}. {[}Accessed: 05-Dec-2016{]}

\hypertarget{ref-ux5fparallelfdtdux5f2016}{}
{[}99{]} ``ParallelFDTD,'' \emph{GitHub}. 2016 {[}Online{]}. Available:
\url{https://github.com/juuli/ParallelFDTD}. {[}Accessed: 05-Dec-2016{]}

\hypertarget{ref-ux5fearux5f2016}{}
{[}100{]} ``Ear,'' \emph{GitHub}. 2016 {[}Online{]}. Available:
\url{https://github.com/aothms/ear}. {[}Accessed: 05-Dec-2016{]}

\hypertarget{ref-schroderux5fraven:ux5f2011}{}
{[}101{]} D. Schröder and M. Vorländer, ``RAVEN: A real-time framework
for the auralization of interactive virtual environments,'' in
\emph{Forum Acusticum}, 2011.

\hypertarget{ref-ux5fpachydermux5f2016}{}
{[}102{]} ``Pachyderm Acoustic,'' \emph{GitHub}. 2016 {[}Online{]}.
Available: \url{https://github.com/PachydermAcoustic}. {[}Accessed:
05-Dec-2016{]}

\hypertarget{ref-ux5fodeonux5f2016}{}
{[}103{]} ``Odeon.'' 2016 {[}Online{]}. Available:
\url{http://www.odeon.dk/}. {[}Accessed: 05-Dec-2016{]}

\hypertarget{ref-ux5fcatt-acousticux5f2016}{}
{[}104{]} ``CATT-Acoustic.'' 2016 {[}Online{]}. Available:
\url{http://www.catt.se/}. {[}Accessed: 05-Dec-2016{]}

\hypertarget{ref-krokstadux5fcalculatingux5f1968}{}
{[}105{]} A. Krokstad, S. Strom, and S. Sørsdal, ``Calculating the
acoustical room response by the use of a ray tracing technique,''
\emph{Journal of Sound and Vibration}, vol. 8, no. 1, pp. 118--125,
1968.

\hypertarget{ref-siltanenux5fraysux5f2010}{}
{[}106{]} S. Siltanen, T. Lokki, and L. Savioja, ``Rays or waves?
Understanding the strengths and weaknesses of computational room
acoustics modeling techniques,'' in \emph{Proceedings of the
International Symposium on Room Acoustics}, 2010.

\hypertarget{ref-svenssonux5fcomputationalux5f2002}{}
{[}107{]} P. Svensson and U. R. Kristiansen, ``Computational modelling
and simulation of acoutic spaces,'' in \emph{Audio Engineering Society
Conference: 22nd International Conference: Virtual, Synthetic, and
Entertainment Audio}, 2002.

\hypertarget{ref-valimakiux5ffiftyux5f2012}{}
{[}108{]} V. Valimaki, J. D. Parker, L. Savioja, J. O. Smith, and J. S.
Abel, ``Fifty years of artificial reverberation,'' \emph{IEEE
Transactions on Audio, Speech, and Language Processing}, vol. 20, no. 5,
pp. 1421--1448, 2012.

\hypertarget{ref-ux5fodeonux5f2016-1}{}
{[}109{]} ``Odeon FAQ.'' 2016 {[}Online{]}. Available:
\url{http://www.odeon.dk/faq-page\#t16n151}. {[}Accessed: 08-Dec-2016{]}

\hypertarget{ref-ux5fvisualux5f2016}{}
{[}110{]} ``Visual Studio support for C++ language features.'' 2016
{[}Online{]}. Available:
\url{https://msdn.microsoft.com/en-us/library/hh567368.aspx}.
{[}Accessed: 09-Dec-2016{]}

\hypertarget{ref-ux5fdownloadux5f2016}{}
{[}111{]} ``Download LLVM releases.'' 2016 {[}Online{]}. Available:
\url{http://llvm.org/releases/}. {[}Accessed: 09-Dec-2016{]}

\hypertarget{ref-ux5fclangux5f2016}{}
{[}112{]} ``Clang support for C++ language features.'' 2016
{[}Online{]}. Available: \url{http://clang.llvm.org/cxx_status.html}.
{[}Accessed: 09-Dec-2016{]}

\hypertarget{ref-ux5fitppux5f2013}{}
{[}113{]} ``ITPP homepage.'' 2013 {[}Online{]}. Available:
\url{http://itpp.sourceforge.net/4.3.1/}. {[}Accessed: 13-Dec-2016{]}

\hypertarget{ref-bottsux5fintegratingux5f2013}{}
{[}114{]} J. Botts and L. Savioja, ``Integrating finite difference
schemes for scalar and vector wave equations,'' in \emph{2013 IEEE
International Conference on Acoustics, Speech and Signal Processing},
2013, pp. 171--175.

\hypertarget{ref-smithux5fiiiux5fequivalenceux5f2004}{}
{[}115{]} J. O. Smith III, ``On the equivalence of the digital waveguide
and finite difference time domain schemes,'' \emph{arXiv preprint
physics/0407032}, 2004.

\hypertarget{ref-yeeux5fnumericalux5f1966}{}
{[}116{]} K. Yee, ``Numerical solution of initial boundary value
problems involving maxwell's equations in isotropic media,'' \emph{IEEE
Transactions on Antennas and Propagation}, vol. 14, no. 3, pp. 302--307,
May 1966.

\hypertarget{ref-murphyux5facousticux5f2007}{}
{[}117{]} D. Murphy, A. Kelloniemi, J. Mullen, and S. Shelley,
``Acoustic modeling using the digital waveguide mesh,'' \emph{IEEE
Signal Processing Magazine}, vol. 24, no. 2, pp. 55--66, 2007.

\hypertarget{ref-sakamotoux5fphase-errorux5f2007}{}
{[}118{]} S. Sakamoto, ``Phase-error analysis of high-order finite
difference time domain scheme and its influence on calculation results
of impulse response in closed sound field,'' \emph{Acoustical Science
and Technology}, vol. 28, no. 5, pp. 295--309, 2007.

\hypertarget{ref-lamux5ftimeux5f2012}{}
{[}119{]} Y. W. Lam and J. A. Hargreaves, ``Time domain modelling of
room acoustics,'' in \emph{Proceedings of the Institute of Acoustics},
2012.

\hypertarget{ref-sheafferux5fphysically-constrainedux5f2012}{}
{[}120{]} J. Sheaffer, M. V. Walstijn, and B. M. Fazenda, ``A
physically-constrained source model for FDTD acoustic simulation,'' in
\emph{Proc. of the 15th Int. Conference on Digital Audio Effects
(DAFx-12)}, 2012.

\hypertarget{ref-aretzux5fcombinedux5f2012}{}
{[}121{]} M. Aretz, \emph{Combined Wave and Ray Based Room Acoustic
Simulations of Small Rooms}. Logos Verlag Berlin GmbH, 2012.

\hypertarget{ref-noisternigux5f3dux5f2003}{}
{[}122{]} M. Noisternig, T. Musil, A. Sontacchi, and R. Holdrich, ``3d
binaural sound reproduction using a virtual ambisonic approach,'' in
\emph{Virtual Environments, Human-Computer Interfaces and Measurement
Systems, 2003. VECIMS'03. 2003 IEEE International Symposium on}, 2003,
pp. 174--178.

\hypertarget{ref-oliverux5flistenux5f2003}{}
{[}123{]} W. Oliver, ``Listen HRTF database.'' 2003 {[}Online{]}.
Available: \url{http://recherche.ircam.fr/equipes/salles/listen/}.
{[}Accessed: 04-Jan-2017{]}

\hypertarget{ref-linkwitzux5factiveux5f1976}{}
{[}124{]} S. H. Linkwitz, ``Active Crossover Networks for Noncoincident
Drivers,'' \emph{Journal of the Audio Engineering Society}, vol. 24, no.
1, pp. 2--8, Feb. 1976 {[}Online{]}. Available:
\url{http://www.aes.org/e-lib/browse.cfm?elib=2649}. {[}Accessed:
05-Jan-2017{]}

\hypertarget{ref-gustafssonux5fdeterminingux5f1994}{}
{[}125{]} F. Gustafsson, ``Determining the initial states in
forward-backward filtering,'' 1994.

\hypertarget{ref-ux5fsonicux5f2017}{}
{[}126{]} ``Sonic Visualiser.'' 2017 {[}Online{]}. Available:
\url{http://sonicvisualiser.org/}. {[}Accessed: 12-Jan-2017{]}

\hypertarget{ref-ux5froomux5f2017}{}
{[}127{]} ``Room EQ Wizard Room Acoustics Software.'' 2017 {[}Online{]}.
Available: \url{https://www.roomeqwizard.com/}. {[}Accessed:
12-Jan-2017{]}

\hypertarget{ref-ux5freverberationux5f2017}{}
{[}128{]} ``Reverberation Time RT60.'' 2017 {[}Online{]}. Available:
\url{http://www.nti-audio.com/en/functions/reverberation-time-rt60.aspx}.
{[}Accessed: 12-Jan-2017{]}

\hypertarget{ref-hodgsonux5fwhenux5f1994}{}
{[}129{]} M. Hodgson, ``When is diffuse-field theory accurate?''
\emph{Canadian Acoustics}, vol. 22, no. 3, pp. 41--42, 1994.

\hypertarget{ref-ux5fassimpux5f2017}{}
{[}130{]} ``Assimp Supported Formats.'' 2017 {[}Online{]}. Available:
\url{http://www.assimp.org/main_features_formats.html}. {[}Accessed:
13-Jan-2017{]}

\hypertarget{ref-ux5foperaticux5f2017}{}
{[}131{]} ``Operatic Voice The Open Acoustic Impulse Response Library.''
2017 {[}Online{]}. Available:
\url{http://www.openairlib.net/anechoicdb/content/operatic-voice}.
{[}Accessed: 16-Jan-2017{]}

\end{document}
